Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-12-07 bayesian-analysis/kundinger-submit.tex
paper at 28 pages.

\begin{figure}[t]
	\begin{center} \includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_speed_plot2} 
		\caption{Run-time for BRL and fabl to run 1000 Gibbs iterations, including hashing step for fabl, for increasing values of both $n_A$ and $n_B$. We see near quadratic growth in runtime for BRL, and near linear growth for fabl.}\label{fig:speed1}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center} \includegraphics[width=0.6\textwidth]{../notes/figures/speed_plot_fixed_nB_slides} 
		\caption{Run-time for BRL and fabl to run 1000 Gibbs iterations, including hashing step for fabl, with increasing $n_A$, and $n_B$ fixed at 500. We see linear growth in runtime for BRL, and near constant runtime for fabl.}\label{fig:speed2}
	\end{center}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot2} 
\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from \cite{sadinle_bayesian_2017}. For each level of overlap and each level of error, we have 100 paired sets of 500 records. We see comparable performance for all levels of error and overlap.}
\label{fig:sadinle_simulation}
	\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
	\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot_partial} 
	\caption{Negative predictive value (NPV) and positive predictive value (PPV) on simulated datasets. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
	\label{fig:sadinle_simulation_partial}
\end{center}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_distribution_smallP_bayes}
		\caption{Posterior distribution and Bayes estimate of overlap across the two files. We note they are quite similar under both methods.}
		\label{fig:overlap-plot}
	\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
	\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_posterior_smallP} 
\caption{Posterior estimates of m parameters with 95\% credible intervals for El Salvador case study. We note they are quite similar across the two methods.}\label{fig:m-and-u}
\label{fig:m-and-u}
\end{center}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.6\textwidth]{../notes/figures/nltcs/overlap_posterior4}
		\caption{Posterior distribution and Bayes estimate of overlap across years 1982 and 1989 of NLTCS data.}
		\label{fig:overlap-plot}
	\end{center}
\end{figure}

@@

@@

	\end{algorithmic}
\end{algorithm}
\clearpage

\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.6\textwidth]{../notes/figures/sim_overlap_trace} 
		\caption{Representative traceplot of overlap between files from simulation study in Section \ref{accuracy}}\label{fig:sim_overlap_trace}
	\end{center}
\end{figure}

\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.6\textwidth]{../notes/figures/sim_m_trace} 
		\caption{Representative traceplot of m parameter from simulation study in Section \ref{accuracy}}\label{fig:sim_m_trace}
	\end{center}
\end{figure}

\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.6\textwidth]{../notes/figures/sim_u_trace} 
		\caption{Representative traceplot of u parameters from simulation study in Section \ref{accuracy}}\label{fig:sim_u_trace}
	\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_trace} 
\caption{Traceplot for number of matches found across datasets in El Salvador case study}\label{fig:overlap_trace}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_trace} 
\caption{Traceplot for m parameter in El Salvador case study}\label{fig:m_trace}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/u_trace} 
\caption{Traceplot for u parameter in El Salvador case study}\label{fig:u_trace}
\end{center}
\end{figure}

>>>>

\begin{figure}[t]
	\begin{center} \includegraphics[width=0.45\textwidth]{../notes/figures/sadinle_speed_plot2} 
		\caption{Run-time for BRL and fabl to run 1000 Gibbs iterations, including hashing step for fabl, for increasing values of both $n_A$ and $n_B$. We see near quadratic growth in runtime for BRL, and near linear growth for fabl.}\label{fig:speed1}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center} \includegraphics[width=0.45\textwidth]{../notes/figures/speed_plot_fixed_nB_slides} 
		\caption{Run-time for BRL and fabl to run 1000 Gibbs iterations, including hashing step for fabl, with increasing $n_A$, and $n_B$ fixed at 500. We see linear growth in runtime for BRL, and near constant runtime for fabl.}\label{fig:speed2}
	\end{center}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
\includegraphics[width=0.5\textwidth]{../notes/figures/sadinle_sim_plot2} 
\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from \cite{sadinle_bayesian_2017}. For each level of overlap and each level of error, we have 100 paired sets of 500 records. We see comparable performance for all levels of error and overlap.}
\label{fig:sadinle_simulation}
	\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
	\includegraphics[width=0.5\textwidth]{../notes/figures/sadinle_sim_plot_partial} 
	\caption{Negative predictive value (NPV) and positive predictive value (PPV) on simulated datasets. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
	\label{fig:sadinle_simulation_partial}
\end{center}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.45\textwidth]{../notes/figures/el_salvador/overlap_distribution_smallP_bayes}
		\caption{Posterior distribution and Bayes estimate of overlap across the two files. We note they are quite similar under both methods.}
		\label{fig:overlap-plot}
	\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
	\includegraphics[width=0.45\textwidth]{../notes/figures/el_salvador/m_posterior_smallP} 
\caption{Posterior estimates of m parameters with 95\% credible intervals for El Salvador case study. We note they are quite similar across the two methods.}\label{fig:m-and-u}
\label{fig:m-and-u}
\end{center}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.45\textwidth]{../notes/figures/nltcs/overlap_posterior4}
		\caption{Posterior distribution and Bayes estimate of overlap across years 1982 and 1989 of NLTCS data.}
		\label{fig:overlap-plot}
	\end{center}
\end{figure}

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.45\textwidth]{../notes/figures/sim_overlap_trace} 
		\caption{Representative traceplot of overlap between files from simulation study in Section \ref{accuracy}}\label{fig:sim_overlap_trace}
	\end{center}
\end{figure}

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.45\textwidth]{../notes/figures/sim_m_trace} 
		\caption{Representative traceplot of m parameter from simulation study in Section \ref{accuracy}}\label{fig:sim_m_trace}
	\end{center}
\end{figure}

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.45\textwidth]{../notes/figures/sim_u_trace} 
		\caption{Representative traceplot of u parameters from simulation study in Section \ref{accuracy}}\label{fig:sim_u_trace}
	\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.45\textwidth]{../notes/figures/el_salvador/overlap_trace} 
\caption{Traceplot for number of matches found across datasets in El Salvador case study}\label{fig:overlap_trace}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.45\textwidth]{../notes/figures/el_salvador/m_trace} 
\caption{Traceplot for m parameter in El Salvador case study}\label{fig:m_trace}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.45\textwidth]{../notes/figures/el_salvador/u_trace} 
\caption{Traceplot for u parameter in El Salvador case study}\label{fig:u_trace}
\end{center}
\end{figure}

@@

	\end{algorithmic}
\end{algorithm}
